Actuator line modeling of vertical-axis turbines

### 2016-05-12 paper.tex
Remove citation; removes about 100 words

NREL has developed and released an actuator line modeling library,
SOWFA~\cite{Churchfield2014b}, for simulating horizontal-axis wind turbine
arrays using the OpenFOAM finite volume CFD library. OpenFOAM is free,
open-source, widely used throughout industry and academia, and has grown a very
active support community around itself \cite{Bachant2015-CFD-online}. Though
SOWFA is also open-source, and has the ability to be coupled to NREL's FAST HAWT
BEM code, its mostly procedural style would have required significant effort and
duplicate code to adapt for cross-flow turbines. Thus, a new and more general
ALM library was developed from the ground up that could model both cross- and
axial-flow turbines, as well as standalone actuator lines. The actuator line
model developed here, dubbed turbinesFoam
\cite{Bachant2016-turbinesFoam-v0.0.7}, was also written as an extension library
for OpenFOAM, and was developed freely and openly from its inception in order to
increase community engagement and research efficiency.

>>>>

NREL has developed and released an actuator line modeling library,
SOWFA~\cite{Churchfield2014b}, for simulating horizontal-axis wind turbine
arrays using the OpenFOAM finite volume CFD library. OpenFOAM is free,
open-source, widely used throughout industry and academia, and has grown a very
active support community around itself. Though SOWFA is also open-source, and
has the ability to be coupled to NREL's FAST HAWT BEM code, its mostly
procedural style would have required significant effort and duplicate code to
adapt for cross-flow turbines. Thus, a new and more general ALM library was
developed from the ground up that could model both cross- and axial-flow
turbines, as well as standalone actuator lines. The actuator line model
developed here, dubbed turbinesFoam \cite{Bachant2016-turbinesFoam-v0.0.7}, was
also written as an extension library for OpenFOAM, and was developed freely and
openly from its inception in order to increase community engagement and research
efficiency.
